%!TEX TS-program = xelatex
%!TEX TS-options = -synctex=1
%!TEX encoding = UTF-8 Unicode
%
%  geach
%
%  Created by Mark Eli Kalderon on 2011-12-26.
%  Copyright (c) 2011. All rights reserved.
%

\documentclass[12pt]{article} 

% Definitions
\newcommand\mykeywords{Dworkin, metaethics} 
\newcommand\myauthor{Mark Eli Kalderon} 
\newcommand\mytitle{Does Metaethics Rest Upon a Mistake?}

% Packages
\usepackage{geometry} \geometry{a4paper} 
\usepackage{url}
\usepackage{txfonts}
\usepackage{color}
\definecolor{gray}{rgb}{0.459,0.438,0.471}
% \usepackage{setspace}
% \doublespace % Uncomment for doublespacing if necessary
% \usepackage{epigraph} % optional

% XeTeX
\usepackage{fontspec}
\usepackage{xltxtra,xunicode}
\defaultfontfeatures{Scale=MatchLowercase,Mapping=tex-text}
\setmainfont{Hoefler Text}
\setsansfont{Gill Sans}
\setmonofont{Inconsolata}

% Bibliography
\usepackage[round]{natbib} 

% Title Information
\title{\mytitle} % For thanks comment this line and uncomment the line below
% \title{\mytitle\thanks{}}% 
\author{\myauthor} 
\date{} % Leave blank for no date, comment out for most recent date

% PDF Stuff
\usepackage[plainpages=false, pdfpagelabels, bookmarksnumbered, backref, pdftitle={\mytitle}, pagebackref, pdfauthor={\myauthor}, pdfkeywords={\mykeywords}, xetex, colorlinks=true, citecolor=gray, linkcolor=gray, urlcolor=gray]{hyperref} 

%%% BEGIN DOCUMENT
\begin{document}

% Title Page
\maketitle

% Main Content

% Layout Settings
\setlength{\parindent}{1em}


\noindent One consequence of the professionalization of philosophy is its ever increasing specialization. Within the normative domain, what has come to be known as metaethical inquiry is increasingly conducted independently of substantive ethical reflection. Even if this trend is intelligible given the economic and institutional pressures that spawned it, it is reasonable to wonder if insights are lost and distortions introduced by focusing exclusively on the limited perspective of metaethical inquiry. Dworkin laments this trend and is skeptical about contempary metaethics.

The division between ``first-order'', ``substantive'' normative inquiry and ``second-order'', ``meta'' normative inquiry has come to seem natural to us and is fundamental to the way we standardly present these topics in our teacing. But it has not always been so. Thus, for example, \citet{Rawls:2000uq} has claimed that the moral philosophies of Hume and Kant cannot intelligibly be presented in this way. Instead, they exemplify what he calls a ``philosophical ethics''. [Characterization of philosophical ethics] 

Dworkin, in the first part of \emph{Justice for Hedgehogs}, presents a distinct alternative to the prevailing orthodoxy. All second-order, meta-normative claims are to be understood, fundamentally, as first-order, substantive, normative claims. If true, then meta-normative inquiry, or what passes for it, could not intelligibly be conducted independently of substantive, normative reflection. If Dworkin is right, then contemporary metaethics rests upon a mistake. (As will emerge, this echo of \citealt{Prichard:1912zm} is deliberate.)

Dworkin's brief against metaethics is a small part of a larger case for the unity of value. The unity of value is the great idea of the book in virtue of which Dworkin counts as a hedgehog set against the prevailing orthodoxy of foxes. The unity of value is not the claim that there exists one master value to which all other values must reduce; rather, it is a distinct value monism that claims that all values are mutually dependent. What it is to be a value of a certain kind will depend upon what it is to be a value of a distinct kind. Consider the following analogy. \citet{Schaffer:2007ma,Schaffer:2008ks,Schaffer:2009vn,Schaffer:2010ja} distinguishes between existence monism, according to which only one thing exists---the world, and priority monism. According to priority monism, the world may contain a plurality of parts, but these parts depend upon the whole whose parts they are. Thus whereas Parmenides is an existence monist---there exists only the one being of the way of truth, Hegel is a priority monist. The unity of value is more akin to priority monism than to existence monism. The analogue of existence monism would be the claim that there exists only one value to which all other values must reduce. In contrast, the unity of value can allow for a plurality of values, it is just that these values are not independent of one another but are rather mutually dependent.

According to the unity of value, distinct values, such as liberty and equality, mutually depend upon one another in such a manner that the reasons they give rise to could not practically conflict. What it is possess liberty presupposes the value of equality: ``You cannot determine what liberty requires without also deciding what distribution of property and opportunity shows equal concern for all'' \citep[4]{Dworkin:2011fk}. But if that is right, then the demands of liberty could not practically conflict with the demands of equality. In this way, the advocate of the unity of value will resist the Pyrhhonian skepticism, revived in modern times by Montaigne, that proceeds from the argument from conflicting values \citep[for a useful to discussion of such argument forms see][]{Annas:1985fk}. As thus far presented, the unity of value is a complex philosophical doctrine, but, as should be clear from the form that Dworkin's skepticism about metaethics takes, and as Dworkin himself insists, it is also a \emph{creed}.

An aspect of the overall case for the unity of value sheds light on Dworkin's skeptical attitude towards metaethics. Specifically, Dworkin's views about the nature of interpretation and the part they play in the argument for the unity of value are relevant to his skepticism about metaethical inquiry. Interpretation, for Dworkin, is an important mode of understanding that finds application in such diverse areas as literary criticism, history, and law. Despite the diversity of application, this mode of understanding nevertheless displays a common structure. \citet[130--134]{Dworkin:2011fk} provides an account of this common structure in his \emph{value theory} of interpretation. According to the value theory of interpretation, there are different genres of interpretation. To interpret something one must first assign it to a particular genre of interpretation. A given genre of interpretation is governed in part by a value or range of values. Thus, for example, in interpreting a poem one may be primarily interested in poetic beauty, say. Thus to interpret something one must second identify the value or values that govern the given genre of interpretation. Finally, one must provide an interpretation that best realizes the governing value or values of the given genre of interpretation. 

Interpretation, on the value theory, is value laden. It is also pervasive---it is a mode of understanding deployed, \emph{inter alia}, in our daily commerce with our fellows. If interpretation is value-laden and pervasive, then since it is an inherently truth-seeking activity, values will themselves be pervasive. Moreover, the values posited by our best interpretations will display a kind of unity. Interpretation is inherently holistic, its methods coherentist. The best interpretation of liberty will make it cohere with equality, and indeed with other important political values. And since interpretation is a truth-seeking activity in virtue of which it counts as a genuine mode of understanding, pervasive values must display the unity required if they are to so cohere.

Let us return to Dworkin's brief against metaethics. Begin with the ordinary view. According to \citet[26-28]{Dworkin:2011fk} we ordinarily take out moral judgements to be true, indeed to be true independently of our judging them to be true. Two questions naturally arise for the ordinary view:
\begin{enumerate}
	\item What makes our moral judgments true?
	\item When are we justified in taking a moral judgment to be true?
\end{enumerate}

Worries that these questions lack adequate answers animates contemporary meta\-ethical discussion. Begin with the first question. What makes our moral judgments true? What do the moral facts consist in? It can seem that the ordinary view is inconsistent with physical or psychological facts making our moral judgments true. But then what \emph{could} make them true? The distribution of morally charged particles? Worries arise with the second question as well. How can we know that a moral judgemnt is true or even be justified in taking a moral jusgement to be true? We don't know the moral facts in the same way that we can know the physical facts. Some physical facts are perceptible, but, on the ordinary view, the moral facts are not perceptible, at least not in the way that some physical facts are. 

These worries motivate skepticism about the ordinary view. \citet[30--33]{Dworkin:2011fk} marks two orthogonal distinctions between, on the one hand, \emph{internal} and \emph{external} skepticism and, on the other hand, \emph{error} and \emph{status} skepticism. The distinction between internal and external skepticism concerns the grounds of such skepticism. Roughly, whereas the internal skeptic relies on the truth of substantive moral claims as premises, the external skeptic relies on second-order claims about morality. The distinction between error and status skepticism concerns the form that such skepticism takes. The error skeptic claims that all moral judgments are false. The status skeptic denies as well that our moral judgments are true but in a different way. Whereas the ordinary view implicitly understands moral judgements as objective descriptions of reality, the status skeptic claims that they have a different status. They function not to describe objective moral reality but have some other, perhaps expressive, function.

These orthogonal distinctions combine in the following manner. Whereas external skepticism may take the form of either an error or status skepticism, internal skepticism may be, at best, a partial error theory since it relies on the truth of a substantive moral claim as a premise. Moreover \citet[33]{Dworkin:2011fk} denies (without explaining) that there could be an internal status skepticism. Dworkin's focus, however, is on external skepticism. The internal skeptic at least agrees with Dworkin that a substantive moral argument is required to call into question the truth of a particular moral claim.

The external skeptic is committed to the existence of a nonmoral argument that our moral judgments are not true (either because they are false or because they are incapable of truth or falisty). This is the mistake upon which, more generally, contemporary metaethics rests. For there is no such sound nonmoral argument. Indeed, this is enshrined in what Dworkin calls \emph{Hume's Principle}: 
\begin{quote}
	[N]o series of propositions about how the world is, as a matter of scientific or metaphysical fact, can provide a succesful case on its own---without some value judgment hidden in the interstices---for any conclusion about what ought to be the case. \citep[44]{Dworkin:2011fk}
\end{quote}
Contrast external skepticism with Dworkin's preferred answer to the two questions about the ordinary view. What makes our moral judgments true is the existence of a sound moral argument for them. Moreover, we are justified in taking a moral judgment to be true when we are justified in taking there to be a sound moral argument for that judgment. These answers are bound to disappoint if one believed that an informative and illuminating answer to these questions must ground morality in something else, if an informative and illuminating answer must take the form of a sound nonmoral argument. This is where the analogy with \citet{Prichard:1912zm} is apt. Prichard and Dworkin oppose philosophical projects that involve knowledge of nonmoral arguments for moral claims, at least if these are to be informative and illuminating. Moreover, each oppose such projects by denying that the relevant knowledge exists---there is no sound nonmoral argument for the truth of morality to be known. They differ only in their reaction to this lack. Prichard suggests that we can know without proof at least certain moral claims. Dworkin, in contrast, claims that moral arguments for moral truth may not count as proof if your standard for proof requires the argument to be nonmoral. But we can nonetheless come to know the truth of moral claims by virtue of possessing a sound moral argument and recognizing it as such. Dworkin's reaction is a manifestation of the coherentism that is constitutively involved in our interpretive practices.

The external skeptic is not alone in making this mistake. A metaphysically ambitious moral realist can agree with the external skeptic that a sound nonmoral argument is needed to establish the truth of a moral claim, it is just that the skeptic's pessimism about the existence of such an argument is here matched by the realist's optimism. The metaphyscially ambitious realist shares the external skeptic's mistake---no such argument is needed and none is to be found.

Let us turn now to Dworkin's case against external skepticism. The position counts as skeptical since it denies the existence of objective moral truth, either because all moral judgements are false or because moral judgments have a non-truth-evaluable status.

% Bibligography
\bibliographystyle{plainnat} 
\bibliography{Philosophy} 

\end{document}